---
title: "Covid-19 Analysis - Midterm Project"
author: "Group 7"
date: "`r Sys.Date()`"
output: html_document
params:
  production: TRUE
---

```{r, set-chunk-opts, echo = FALSE, eval = params$production}
library(knitr)
opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE
)
```


# Midterm Project Introduction

- This report analyzes data on 209,715 COVID-19 patients from the Mexican government, focusing on mortality predictors. Among the population, 93% survived, and 7% succumbed, emphasizing COVID-19's severe impact.

- Key analyses include Table 1, which compares patient characteristics between survivors and non-survivors, and a heatmap highlighting correlations between comorbidities and outcomes, with conditions like pneumonia, COPD, diabetes, hypertension, and chronic renal disease strongly linked to mortality. A boxplot further visualizes these associations.

- Logistic regression models were developed to identify mortality predictors. The optimized model, incorporating variables such as age, comorbidities, and interventions, provides a robust framework for understanding risk factors among COVID-19 patients.

```{r, here-i-am, include = FALSE}
here::i_am(
  "report_group7.Rmd"
)
```


```{r, load-data}
data <- readRDS(
  file = here::here("data/covid_data_cleaned.rds")
)
```

# Descriptive Analysis

## Tabular analysis

##### Table 1: Descriptive summary table

Table 1 provides a detailed comparison of patient characteristics and clinical factors associated with death among COVID-19 patients in the analyzed subset of the Mexican COVID-19 dataset. The dataset includes 209,715 patients, of which 194,444 (93%) survived, and 15,271 (7%) died. Significant differences were observed across all variables between the two groups, as indicated by p-values < 0.001 for most comparisons. These findings underscore the importance of early identification of high-risk groups to optimize care and resource allocation during the pandemic.

```{r, table1}
table1 <- readRDS(
  file = here::here("table/table1.rds")
)
table1
```

## Graphical analysis

##### Heatmap

The heatmap illustrates the correlations between various comorbidities and death across the entire dataset. Patients with pneumonia exhibit the strongest positive correlation with death at 0.45. Diabetes (0.23), hypertension (0.22), chronic renal disease (0.13), and chronic obstructive pulmonary disease (0.10) also show moderate positive correlations with death.

```{r, load-plots}
#| fig.align = "center",
#| out.width = "600px"
knitr::include_graphics(
  here::here("figure", "Overall Comorbidities & Death.rds") 
)

```

##### Plots

The boxplots visualize the relationship between Pneumonia, Diabetes, Hypertension, Renal Chronic Disease, and COPD (which were identified as the comobidities with the strongest positive correlation to death) and the outcome variable, Death. Each comorbidity is treated as a categorical variable with two levels (e.g., "Yes" and "No"), and the boxplots show the distribution of death status (0 = Alive, 1 = Death) for each comorbidity. 

```{r, load-boxplots}
#|fig.align = "center"
#|out.width = "600px"
knitr::include_graphics(
  here::here("figure", "Comorbidities with the Strongest Positive Correlation to Death.rds")
)
```

# Regression Analysis

We tried to fit a logistic regression model on covariates that have statistically significant impact on survival. After assessing the full model, DIABETES, CARDIOVASCULAR, OBESITY, MEDICAL_UNIT is removed from our model and our finalized model is derived as follows:

```{r, regression}
regression_output <- readRDS(
  file = here::here("output/optimized_model.rds")
)
regression_output
```


