---
title: "Covid-19 Analysis - Midterm Project"
author: "Group 7"
date: "`r Sys.Date()`"
output: html_document
params:
  production: TRUE
---

```{r, set-chunk-opts, echo = FALSE, eval = params$production}
library(knitr)
opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE
)
```


# Midterm Project Introduction

**Description**

**Predictors**
  
**Objective:**

```{r, here-i-am, include = FALSE}
here::i_am(
  "report_group7.Rmd"
)
```


```{r, load-data}
data <- readRDS(
  file = here::here("data/covid_data_cleaned.rds")
)

```

# Descriptive Analysis

## Tabular analysis

##### Table 1: Descriptive summary table

description

```{r, table1}
table1 <- readRDS(
  file = here::here("table/table1.rds")
)
table1
```

## Graphical analysis

##### Heatmap

The heatmap illustrates the correlations between various comorbidities and death across the entire dataset. Patients with pneumonia exhibit the strongest positive correlation with death at 0.45. Diabetes (0.23), hypertension (0.22), chronic renal disease (0.13), and chronic obstructive pulmonary disease (0.10) also show moderate positive correlations with death.

```{r, load-plots}
#| fig.align = "center",
#| out.width = "600px"
knitr::include_graphics(
  here::here("figure", "Overall Comorbidities & Death.rds") 
)

```

##### Plots

description

```{r, load-plots}
#| fig.align = "center",
#| out.width = "600px"
knitr::include_graphics(
  here::here("figure/name.png")
)
```

# Survivial Analysis


