---
title: "Covid-19 Analysis - Midterm Project"
author: "Group 7"
date: "`r Sys.Date()`"
output: html_document
params:
  production: TRUE
---

```{r, set-chunk-opts, echo = FALSE, eval = params$production}
library(knitr)
opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE
)
```


# Midterm Project Introduction

**Description**

**Predictors**
  
**Objective:**

```{r, here-i-am, include = FALSE}
here::i_am(
  "report_group7.Rmd"
)
```


```{r, load-data}
data <- readRDS(
  file = here::here("data/covid_data_cleaned.rds")
)

```

# Descriptive Analysis

## Tabular analysis

##### Table 1: Descriptive summary table

Table 1 provides a detailed comparison of patient characteristics and clinical factors associated with death among COVID-19 patients in the analyzed subset of the Mexican COVID-19 dataset. The dataset includes 209,715 patients, of which 194,444 (93%) survived, and 15,271 (7%) died. Significant differences were observed across all variables between the two groups, as indicated by p-values < 0.001 for most comparisons. These findings underscore the importance of early identification of high-risk groups to optimize care and resource allocation during the pandemic.

```{r, table1}
table1 <- readRDS(
  file = here::here("table/table1.rds")
)
table1
```

## Graphical analysis

##### Heatmap

The heatmap illustrates the correlations between various comorbidities and death across the entire dataset. Patients with pneumonia exhibit the strongest positive correlation with death at 0.45. Diabetes (0.23), hypertension (0.22), chronic renal disease (0.13), and chronic obstructive pulmonary disease (0.10) also show moderate positive correlations with death.

```{r, load-plots}
#| fig.align = "center",
#| out.width = "600px"
knitr::include_graphics(
  here::here("figure", "Overall Comorbidities & Death.rds") 
)

```

##### Plots

description

```{r, load-plots}
#| fig.align = "center",
#| out.width = "600px"
knitr::include_graphics(
  here::here("figure/name.png")
)
```

# Survivial Analysis


